\chapter{Affordable Source of PCPA (Fenclonine)}
\tags{Fenclonine, PCPA, Pharmaceutical Drugs, Supplier}
\info{THREAD \#3099~\textbar{}~JANUARY 29, 2014}

\begin{refsection}

Hi all,

There has been a lot of interest from members of this forum (including myself) to get our hands on the legendary substance PCPA (p-chlorophenylalanine), which will selectively and potently inhibit tryptophan hydroxylase and thus lower serotonin. Ray has written about its effects on sexuality/libido, but if you search PubMed you will see that it has a lot of other benefits including IBS/IBD, Crohn's, osteoporosis, heart failure, cognition, MS, etc.

Anyways, long story short---after searching for months for a reliable source that does not charge an arm and a leg, I think I may have found one. Here is the link.\textsuperscript{\cite{url834e860b}}

I am placing an order for 25 g and will give it a try. The human dosage seems to be in the range 2 g--4 g per day, so I will start with 2 g a day and take it until I run out. In the human studies, effects were evident within 24--48 hours so I should be able to feel the change.

If someone else is willing to take the plunge and try it out as well maybe we can get the supplier to even give us a discount. I saw something on their website that they may offer up to 30\% off to regular clients.

I am really excited about this find. This has been my Unicorn of all things Peat, so maybe the search is over!

\printbibliography[heading=subbibliography]

\end{refsection}