\chapter{CDC---Iatrogenic Deaths \enquote{Disappeared} in 2020, COVID-19 Took Their Place}
\tags{CDC, CNN, COVID-19, Deaths, Fraud, Genocide, Iatrogenic, Scam}
\info{THREAD \#39536~\textbar{}~MARCH 31, 2021}

\begin{refsection}

As many forum users know, for decades up until 2020 CDC annual reports listed medical error (iatrogenic) deaths as the third-leading cause of death in the US. The only change in that annual \enquote{ranking} of deaths was in the last 5 years cancer sometimes overtaking heart disease as a leading cause of death in the US and most other Western (\enquote{developed}) countries. Now, the latest CDC report has completely removed the iatrogenic category, and COVID-19 deaths have taken that third place. If the CDC had simply moved the iatrogenic deaths up or down the list, it would have been at least a debatable issue. However, the complete disappearance of medical error deaths exposes directly the fraud. Iatrogenic deaths can't just vanish in a single year. In fact, if the hospitals were full to brim with patients in 2020 then iatrogenic deaths would be much higher than prior years. BTW, the \enquote{unintentional injury} category on 4th place covers \enquote{life accidents.} They are counted separately from iatrogenic deaths, so one cannot argue that iatrogenic deaths moved to 4th place.

Unless I am missing something, this may be the most direct admission yet by the powers that be that the COVID-19 death numbers are completely fake. Either no COVID-19 deaths occurred in 2020 or all of them were iatrogenic in nature so one can swap the names on 3rd place. So, either we have a blatant, public, demonstrable and irrefutable lie or public admission by CDC of genocidal medical interventions for all COVID-19 patients who died in hospitals in 2020.\textsuperscript{\cite{urlfe446e23}}

\begin{tcolorbox}[quote]

Heart disease

Cancer

\underLine{\textsb{COVID-19}}

Unintentional injury

Stroke

Chronic lower respiratory disease

Alzheimer's disease

Diabetes

Influenza and pneumonia

Kidney disease\textsuperscript{\cite{url10239uydn}}

\end{tcolorbox}

And here is the evidence that up until 2020 iatrogenic deaths were the third-leading cause of death in the US.\textsuperscript{\cite{url91823hbw, url218903ha}}

\begin{tcolorbox}[quote]

\dots{}Recent studies of medical errors have estimated errors may account for as many as 251,000 deaths annually \underLine{\textsb{in the United States (U.S.), making medical errors the third leading cause of death}}.\textsuperscript{\cite{url0123hone}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}