\chapter{CDC: We Have No Idea How Many Are Vaxxed/Unvaxxed in the USA}
\tags{CDC, COVID-19, Fraud, Pandemic, Scam, Statistics, Vaccines}
\info{THREAD \#44329~\textbar{}~DECEMBER 19, 2021}

\begin{refsection}

\dots{}And, more importantly, it is probably the first direct official admission at such a high level that the number of vaxxed has been (grossly?) overestimated. By how much? Well, CDC doesn't know\dots{} and is no hurry to find out. Probably, so that mainstream media can continue to gaslight the public that majority of Americans are vaxxed, and the unvaxxed are only a tiny, fringe group of lunatics.

I bet the story is not much different in other countries, especially the EU, UK, Canada, Australia, etc. Apparently, no official stats coming out from the govt can be trusted, which seems to be an opinion that even some govt officials themselves are holding.

\begin{tcolorbox}[quote]

\dots{}The US Centers for Disease Control has overcounted the number of Americans who have received COVID-19 vaccines, recording numerous second doses and boosters as first shots, state officials told Bloomberg. While the CDC's data suggests some 240 million Americans have received at least one shot, the statistics claim just 203 million are fully vaccinated, a statistic which would suggest 37 million Americans started---but did not finish---their course of injections. However, state and local officials who spoke to Bloomberg on Saturday found those numbers \enquote{\underLine{\textsb{improbable}},} suggesting instead that \underLine{\textsb{the government had incorrectly recorded Americans' vaccine data on a grand scale, mis-counting second doses and booster shots as first doses and thus overestimating the number of vaccinated Americans altogether}}.\textsuperscript{\cite{url90ycv2k1}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}\enquote{\underLine{\textsb{We don't have any faith in the numbers on the CDC website, and we never refer to them,} Philadelphia Department of Public Health spokesman James Garrow told Bloomberg}}. The state of Pennsylvania lowered its estimate for adults who'd received one shot from 98.9\% to 94.6\% last month, and plans to submit another round of revised figures by the end of the year. The state of Illinois found it had overcounted both the unvaccinated and the fully-vaccinated---with 540,000 more unvaxxed over the age of 12 and 730,000 totally vaccinated who had somehow been skipped in previous counts. While the official statistics appear to indicate the US---with 72.5\% of its population having received at least one shot but just 61.3\% fully-vaxxed---is a major outlier compared to other Group of Seven countries, the discrepancy is more likely to be due to the fragmentation of recordkeeping. \underLine{\textsb{According to Bloomberg's statistics, the European Union has just a 2.6\% gap between the singly-vaxxed and the fully-jabbed, and while the US has the largest disparity at 11\%, the UK is second among G7 nations with a 6.7\% gap}}.\textsuperscript{\cite{url90ycv2k1}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}If changes are made to the national data on the scale of Pennsylvania's revisions, this would mean increasing the number of Americans who are unvaccinated by more than 10MM. \enquote{\underLine{\textsb{The truth is, we have no idea}},} said Clay Marsh, West Virginia's Covid czar.\textsuperscript{\cite{url90ycv2k1}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}