\chapter{CNN: The COVID-19 Vaccines Do Not Prevent Infection}
\tags{CNN, COVID-19, Fraud, Infection, MSM, Pandemic, Scam, Vaccines}
\info{THREAD \#38526~\textbar{}~JANUARY 30, 2021}

\begin{refsection}

A few weeks ago I posted an op-ed in the prestigious \textit{BMJ} discussing how the COVID-19 vaccines trials are almost pointless as they are not designed to test if the vaccines would prevent development of COVID-19, exacerbations of COVID-19, hospitalizations, or deaths. The trials were apparently designed to test only whether the vaccine would lower risk of infection with SARS-CoV-2.

In that post above, I mentioned that the public health authorities are, of course, ignoring the trial design and gaslighting the public every chance they get that the vaccines are the key to safety. Now, a CNN article states directly that the vaccines do not really prevent infection but again claims that they prevent developing COVID-19. Again, the latter claim is not based on any evidence and none of the vaccine trials provide evidence for such claims. I guess the more interesting part here is this---if CNN is now admitting that the vaccines do not really prevent infection (which was the primary goal of the vaccine trials conducted so far) then what \enquote{benefit} are these vaccines supposed to provide?

\begin{tcolorbox}[quote]

\dots{}\underLine{\textsb{COVID-19 vaccines prevent illness, but do not necessarily prevent infection}}. If someone tests positive and doesn't get sick, the vaccine has worked as intended. If someone tests positive within a few weeks of receiving the second dose, it may be because the vaccine hasn't yet fully kicked in.\textsuperscript{\cite{urlasd98yw}}

\end{tcolorbox}

Ironically, the CNN article is about a politician who got infected with SARS-CoV-2 after getting \underLine{\textsb{both}} vaccine shots. I guess the house of cards is starting to shake/collapse, so CNN and MSM are quick to change the narrative even if the new narrative is a blatant lie\dots{}


\printbibliography[heading=subbibliography]

\end{refsection}