\chapter{Cuomo Says NY Must Reopen ASAP or They Will Be Nothing Left to Reopen}
\tags{Biden, Charade, Cuomo, Election, Fraud, Infection, Lockdown, New York, Politics, Reopen, Scam, Trump, Vaccines, Virus}
\info{THREAD \#38244~\textbar{}~JANUARY 13, 2021}

\begin{refsection}

A year ago, if I had seen an article like that on MSM I would have just rolled my eyes and assumed it was just schizophrenic journalists writing in a state of SSRI withdrawal. Yet, here it is and it is not an isolated news item. After an entire year of mocking, vilifying, arresting, doxxing, cancelling, etc. of people who were saying all along lockdowns will decimate the country, Cuomo is now singing that same song. Namely, if NY does not reopen ASAP the economic devastation would be so complete there will be nothing left to reopen. Just a week ago, Cuomo was foaming at the mouth then asked when NY will reopen and said that considering the skyrocketing infection rate numbers, \underLine{\textsb{and the very low vaccination rates}}, reopening even in 2022 was actually an optimistic goal. This whole thing is now about to be over (as if it never happened) as soon as the election is done and powers that be got their guy installed as President. Even the vaccine may turn out to be a very small piece of the political puzzle. Yes, a lot of companies/people will get rich off of it and it is a nice \enquote{gig} for people like Gates, but it is not really a factor in reopening anything. California already put a recall on the ballot, because Newsom messed things up beyond belief. I am not sure why the same is not already under way in NY too\dots{}

What a travesty this world has become!

\begin{tcolorbox}[quote]

\dots{}\underLine{\textsb{New York Governor Andrew Cuomo said Monday that the state must start reopening its economy despite most New Yorkers not having received a coronavirus vaccination, saying that there will be \enquote{nothing left to open} otherwise}}\dots{} New York currently does not allow gatherings of more than ten people at private residences. Indoor dining at restaurants is limited and even prohibited in some areas with higher positivity rates.\textsuperscript{\cite{urlas09dfyu}}

\end{tcolorbox}


\printbibliography[heading=subbibliography]

\end{refsection}