\chapter{Italy Admits 97\%+ of COVID-19 Deaths Were Not From the Virus}
\tags{Co-Morbidity, COVID-19, Death, Fraud, Italy, Mind Control, Pandemic, SARS-CoV-2}
\info{THREAD \#43525~\textbar{}~NOVEMBER 05, 2021}

\begin{refsection}

There you have it---once the definition of a \enquote{COVID-19 death} is changed from \enquote{died \underLine{\textsb{with}} COVID-19} to \enquote{died \underLine{\textsb{from}} COVID-19,} more than 97\% of the officially reported COVID-19 deaths disappear, at least in Italy. In the US, the situation is quite similar, as per official CDC stats---i.e., only \char`~6\% of the officially reported COVID-19 deaths were from COVID-19. The other \char`~94\% died with COVID-19, plus 3--4 serious chronic conditions, advanced age, or even traffic accidents. In other words, as the Italians themselves state, COVID-19 has killed significantly FEWER people than the seasonal flu! Open fraud aside, the even more damning part is that various governments, such as UK, have admitted publicly to deliberately manipulating and scaring the public using the fake numbers and advanced psychological warfare techniques legalized \underLine{\textsb{only}} for military personnel and \underLine{\textsb{only}} when targeting foreign adversaries. Yet, apparently we, as societies, have become so accustomed to constant fraud and corruption within our governments that the charade continues unabated and in the minds of at least half of the population in Western countries, the scary \enquote{pandemic} is still \enquote{raging on.} Another explanation is that, as Peat mentioned himself, societies have become very psychopathic over the last few decades and now even such atrocities are brushed aside as long as they (appear to) benefit financially a significant portion of the population.

\begin{tcolorbox}[quote]

\dots{}Italian newspaper Il Tempo\textsuperscript{\cite{url783563ba}} reports that the Institute has \underLine{\textsb{revised downward the number of people who have died from COVID rather than with COVID from 130,000 to under 4,000}}.

\begin{quote}

\enquote{\underLine{\textsb{Yes, you read that right. Turns out 97.1\% of deaths hitherto attributed to Covid were not due directly to Covid}},} writes\textsuperscript{\cite{urld6b0b18e}} Toby Young.

\end{quote}

Of the of the 130,468 deaths registered as official COVID deaths since the start of the pandemic, only 3,783 are directly attributable to the virus alone.

\begin{quote}

\enquote{\underLine{\textsb{All the other Italians who lost their lives had from between one and five pre-existing diseases}}. Of those aged over 67 who died, 7\% had more than three co-morbidities, and 18\% at least two,} writes Young.

According to the Institute, 65.8\% of Italians who died after being infected with Covid were ill with arterial hypertension (high blood pressure), 23.5\% had dementia, 29.3\% had diabetes, and 24.8\% atrial fibrillation. Add to that, 17.4\% had lung problems, 16.3\% had had cancer in the last five years and 15.7\% suffered from previous heart failures.

\end{quote}

\underLine{\textsb{The Institute's new definition of a COVID death means that COVID has killed fewer people in Italy than (whisper it) the average bout of seasonal flu}}. If a similar change were made by other national governments, the official COVID death toll would be cut by a margin of greater than 90 percent. Don't expect many others to follow suit though, given that governments have invested so much of their authority in hyping the the threat posed by the virus. For example, \underLine{\textsb{behavioral psychologists in the UK worked with the state to deliberately \enquote{exaggerate} the threat of COVID via \enquote{unethical} and \enquote{totalitarian} methods of propaganda in order to terrify the public into mass compliance. And it worked}}.\textsuperscript{\cite{url2309o8ih}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}