\chapter{More Than 94\% of UK Adults Have COVID-19 Antibodies}
\tags{Antibodies, Coronavirus, COVID-19, Herd Immunity, Immunity, Natural, SARS-CoV-2, UK}
\info{THREAD \#42085~\textbar{}~AUGUST 19, 2021}

\begin{refsection}

A shocking news article, which would have immediately ended any discussions about lockdowns, social distancing, vaccine passports, etc. due to herd immunity\dots{} if it was published back in early 2020, but not now. Why? Well, the powers that be have changed the definition of herd immunity and now this gift from the gods is only available to us through vaccination, not natural immunity. Yet, a study published just a few days ago demonstrated the vaccines are both no more than 40\%--50\% effective and also providing \enquote{immunity} that lasts much shorter than the naturally acquired antibodies through catching the virus. The travesty of the article about UK is that it tries to explain the high levels of population immunity due to the vaccination. What a convenient way to conceal that most Western countries likely already have natural herd immunity, and some of them probably had it as early as mid-2020?!

Let's see if UK govt will have the nerve to impose another lockdown this fall, and whether (considering these numbers on immunity) the UK population will go along with the narrative this time. I bet the same level of immunity is also present in Australia and NZ, yet the lockdowns there continue and in NZ they were implemented again after just a \underLine{\textsb{single}} positive case was recorded last week.\textsuperscript{\cite{url91238g0h}}

\begin{tcolorbox}[quote]

\dots{}\underLine{\textsb{A staggering 94.2\% of adults in England have antibodies for COVID-19, according to a new report from the UK's}} Office of National Statistics.\textsuperscript{\cite{url7243d0b8}} Roughly 80.7\% of England's population has been fully vaccinated, suggesting the rest of the 94.2\% acquired antibodies through natural infection with the coronavirus. The report is great news for England, which has seen COVID-19 rates plateau at roughly 25,000 per day. Deaths have remained extremely low, with a seven-day average of 81 COVID-19 fatalities daily.\textsuperscript{\cite{urlas0dc8yhs}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}