\chapter{Pentagon Creates MICROCHIP That Will Detect COVID-19 Under Skin}
\tags{Chip, Conspiracy, COVID-19, Dictatorship, Embedded, Microchip, Surveillance, Tracking, Transhumanism}
\info{THREAD \#39749~\textbar{}~APRIL 12, 2021}

\begin{refsection}

So much for the chipping, tagging and tracking us all the time being nothing but a bizarre ideation in the heads of paranoid people. Of course, the first version of the chip is simply for \enquote{saving} your life from the evil, scary COVID-19. However, just like the mRNA vaccines, the chip is not a final product but a \enquote{platform} that can have a wide variety of functionality uploaded onto it as needed. If this news was not already sinister enough, one of Bill Gates' companies has a contract with DARPA to produce exactly such technology for DoD. If this chip turns out to have been designed by Gates' outfits, he should be immediately indicted for multiple felonies, including lying under oath to Congress and various other federal officials who asked for his testimony on the subject of vaccines, chips, etc. Gates vehemently denied that he or his companies were in any way involved in designing, producing or even consulting the govt. about such technologies.

Notice that they say the chip is not in wide use outside of DoD, which suggests that it is being actively tested/used within DoD, using soldiers as guinea pigs since most of them have signed their rights away upon enlisting.

\begin{tcolorbox}[quote]

\dots{}\underLine{\textsb{Medical researchers working for the Pentagon have claimed to have created a microchip that can identify viruses like COVID-19 if they are under your skin}}. Retired Army Col. Dr. Matt Hepburn, an infectious disease physician, told \enquote{60 Minutes} that \underLine{\textsb{the microchip acts like a \enquote{check engine} light for people, but does not track their every movement, which has been central to online conspiracy theories about COVID-19 vaccinations}}.\textsuperscript{\cite{urldsa09yu2}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}\underLine{\textsb{The microchip, which is not in widespread use beyond the Defense Department, is embedded under the skin in a tissue-like gel and continuously tests the recipient's blood for evidence of a virus, like COVID-19}}. \underLine{\textsb{Once detected, it alerts the carrier they must immediately get a blood test}}. \underLine{\textsb{\enquote{It's a sensor,}}} Hepburn said. \underLine{\textsb{\enquote{That tiny green thing in there, you put it underneath your skin and what that tells you is that there are chemical reactions going on inside the body and that signal means you are going to have symptoms tomorrow}}.} He went on to claim that the early detection technology could \underLine{\textsb{\enquote{stop the infection in its tracks}}.} Another bit of technology highlighted during the \enquote{60 Minutes} segment that could directly affect viruses like Covid was \underLine{\textsb{a dialysis machine that would be used to filter and detox blood and then reinsert the blood into a patient until the virus is removed from the body}}.\textsuperscript{\cite{urldsa09yu2}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}