\chapter{Rising Use of Methylene Blue in India as COVID-19 Prevention/Treatment}
\tags{Antiviral, COVID-19, India, Methylene Blue, Pandemic, Prevention, Treatment}
\info{THREAD \#40040~\textbar{}~APRIL 26, 2021}

\begin{refsection}

As it appears, the general population is starting waking up. In addition to news about India, I also noticed that most methylene blue (MB) vendors on Amazon are commonly sold out or have messages saying the product is \enquote{unavailable.} Large chemical suppliers like Sigma Aldrich are also routinely sold out, even of the reagent grade products, which are not for human consumption. If the use of MB in the general population continues to rise, we may see attempts to regulate/ban it. Since it is technically a prescription drug for methemoglobinemia and shock, it can easily get enforcement action from FDA if their pharma friends complain that MB is eating into their vaccine sales.

\begin{tcolorbox}[quote]

\dots{}Almost everyone would have come across some or another initiative through which re-usable masks, gloves, sanitizers, ayurvedic \enquote{kadhas} or homeopathic arsenic album gets distributed free in the ongoing COVID-19 induced pandemic. But, \underLine{\textsb{appearences of methylene blue bottles outside houses of quarantined people have puzzled many}}. \underLine{\textsb{Some residents have even started consuming it as a \enquote{wonder liquid} to keep themselves safe from the dreaded infection}}. \enquote{A week ago, \underLine{\textsb{an unknown organization simply arrived in our society and kept such bottle outside our house asking us to start taking its doses}}. Since, there was no mention of the supplier, the manufacturer, the doctor who prescribed it or even other literature, I got suspicious. My doctor friend warned me against its usage without doctor's consultation,} said Kavita Vasan, a Gotri resident. Even as the mother of a two-and-a-half-year-old kid has strictly gone by doctor's advice, others in her society have started consuming it.\textsuperscript{\cite{urlsad09u2s}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}\enquote{some of them seem to have got addicted to it. They are taking it even as they are not having any Covid symptom,} she said. \underLine{\textsb{Though it is not part of the COVID-19 management protocol, there are certain doctor who see a use for it}}. Last year, \underLine{\textsb{Dr. Deepak Golwakar, a senior pulmonologist from Bhavnagar, with over four decades of clinical experience, had started advocating its use}}. Golwakar's supporters back him to the hilt. Despite several attempts, TOI could not contact Golwakar.\textsuperscript{\cite{urlsad09u2s}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}