\chapter{CDC Refuses to Release COVID-19 Info Because the Public May \enquote{Misinterpret} It}
\tags{CDC, COVID-19, Disinformation, Effectiveness, Fraud, Mortality, Pandemic, Safety, Stats, Vaccine}
\info{THREAD \#45301~\textbar{}~FEBRUARY 21, 2022}

\begin{refsection}

The CDC has now surpassed its buddies over at the CIA and refuses to release even public, non-classified pandemic data covering mortality, gender, age, vaccination status, co-morbidities, etc. Why mentioning the CIA? Well, some years ago the CIA refused to release declassified information on the Bay of Pigs invasion as it may \enquote{confuse} the public and people may \enquote{misinterpret} it. I doubt two of the biggest agencies within the US govt are using identical language in regards to very similarly nefarious events without this being standard procedure and also an indication of the the bombshells the concealed information contains.

\begin{tcolorbox}[quote]

\dots{}Fifty-one years after the failed attempt to invade Cuba, the Central Intelligence Agency and Department of Justice continue to claim that releasing the final volume of a CIA history of the debacle would \enquote{\underLine{\textsb{confuse the public}}} and should therefore remain withheld.\textsuperscript{\cite{url912bksd9}}

\end{tcolorbox}

Without that data CDC is now refusing to publish, it is virtually impossible to judge vaccine effectiveness (and safety) and the only data publicly available are the pharma-sponsored studies. Needless to say, those are not exactly reliable. When asked why it is refusing to release the data, which is public and must be released by law, CDC stated that the information \enquote{\dots{}\underLine{\textsb{might be misinterpreted as the vaccines being ineffective}}.} BINGO! To me, the CDC just admitted what we have been discussing on the forum since the clotshots first became available in late 2020.

Furthermore, as it turns out the COVID-19 data published by CDC so far is a tiny fraction of what CDC has collected since the start of the \enquote{pandemic} in March 2020. You can safely assume whatever has been publicly released is undoubtedly cherry-picked to favor vaccines, show severity of COVID-19, benefit of lockdowns, etc. Keep in mind that CDC has not yet released even the final raw mortality data for neither 2020 nor 2021. The raw numbers released for those years are provisional and subject to change, in CDC's own words. The only data the CDC considers final is the so-called \enquote{excess mortality.} That is actually a contradiction of terms, as \enquote{excess mortality} is based on a model and can never be truly final since it does not correspond to anything real. Also, such model-based data easily be massaged to show whatever the CDC wants. Unsurprisingly, CDC keeps mentioning only the \enquote{excess mortality} in its propaganda materials, and has even dropped the word \enquote{excess,} so that most people hearing/reading the propaganda would walk away with the impression that those numbers are solid, raw death numbers when in fact they are mostly imaginary (just a model).

So, it looks like CDC is basically keeping all the juicy info on the \enquote{pandemic} to itself. Unless somebody sues, just as in the case of Pfizer vaccine data, CDC won't release that information even though it is most likely required to do so by federal law. Even if somebody sues, CDC will probably try to pull the same trick as FDA and claim it can release the data no earlier than 2075 due to staff shortages. And since the court in which that case would be decided is probably different from the one in which the FDA cases was decided there is a good chance the CDC may get its wish.\textsuperscript{\cite{urlodhbsd09, url91ee8196}}

\begin{tcolorbox}[quote]

\dots{}The US Centers for Disease Control and Prevention \underLine{\textsb{(CDC) has kept reams of its COVID-19 data under wraps for more than a year}}, the New York Times reports, \underLine{\textsb{holding back figures at least partly because it doesn't trust the public to interpret the information correctly}}. The agency's seemingly selective disclosure came to light\textsuperscript{\cite{url91ee8196}} in an article by the Times on Sunday. Among the data being withheld is a breakdown of COVID-19 hospitalizations by age, race, and vaccination status. The CDC also chose not to report on such findings as the efficacy of booster shots in 18- to 49-year-olds, even though it collected the information, the article added. Although it's the agency leading America's COVID-19 response, \underLine{\textsb{the CDC has published only a \enquote{tiny fraction} of the data that it has collected}}, the Times said. In lieu of US data being made more widely available, experts were forced to look elsewhere for information---such as Israeli figures on booster shots---that would help them make informed recommendations.\textsuperscript{\cite{url923bnksd}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}Such omissions have included figures on COVID-19 infections among fully vaccinated Americans. According to the media report, the \underLine{\textsb{CDC has been reluctant to publish those figures because \enquote{they might be misinterpreted as the vaccines being ineffective}}.} \underLine{\textsb{Nordlund confirmed that concern as one of the reasons}}. Epidemiologist Jessica Malaty Rivera, part of an independent COVID-19 data-tracking project, told the Times that her group had been begging for such information for two years. \enquote{We are at much greater risk of misinterpreting the data with data vacuums than sharing the data with proper science, communication and caveats,} she argued.\textsuperscript{\cite{url923bnksd}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}