\chapter{Another COVID-19 Vaccine Trial Halted Due to Serious Side Effects}
\tags{Coronavirus, COVID-19, Dangerous, Halted, Safety, Serious Adverse Event, Side Effect, Trial, Vaccines}
\info{THREAD \#36821~\textbar{}~OCTOBER 13, 2020}

\begin{refsection}

At this point, two out of the four Phase III human clinical trials for COVID-19 vaccine have been halted due to safety concerns as a result of serious adverse events (SAE) in the active group(s). Here is the thread about the other one being halted.\textsuperscript{\cite{url43235527}}

Neither one of those halted trials has resumed (in the US), which speaks volumes about the \enquote{safety} of the vaccine. The really suspicious thing is that unlike the first SAE issue this time they are not releasing information as to what the SAE event is/was. This usually means the issue is very serious (possibly lethal) so they are giving themselves time to formulate a PR \enquote{strategy} and scrambling to find other causes on which to blame the SAE.

\begin{tcolorbox}[quote]

\dots{}Johnson \& Johnson's Janssen vaccine arm is developing the shot. \underLine{\textsb{The company did not say what the unexplained illness was}}, but one point of clinical trials is to find out if vaccines cause dangerous side effects. Trials are stopped when they pop up while doctors check to see if the illness can be linked to the vaccine or is a coincidence.\textsuperscript{\cite{urla887dece}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}\enquote{\underLine{\textsb{We must respect this participant's privacy}}. \underLine{\textsb{We're also learning more about this participant's illness}}, and it's important to have all the facts before we share additional information,} the company added.\textsuperscript{\cite{urla887dece}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}\underLine{\textsb{This is the second Phase 3 coronavirus vaccine trial to be paused in the US}}. \underLine{\textsb{AstraZeneca's vaccine trial was paused last month because of a neurological complication in a volunteer in Britain}}. While the trial resumed there and in other countries, \underLine{\textsb{it remains paused in the United States while the US Food and Drug Administration investigates}}.\textsuperscript{\cite{urla887dece}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}