\chapter{COVID-19 Vaccine Trials Are Essentially Pointless}
\tags{Coronavirus, COVID-19, Fraud, Pandemic, Pointless, Scam, Trial, Vaccines}
\info{THREAD \#36952~\textbar{}~OCTOBER 21, 2020}

\begin{refsection}

\dots{}Because they won't tell us if the vaccines can prevent deaths or serious COVID-19 complications, or virus transmission between people. If you think I am trolling, check out the CNN and \textit{BMJ} articles below---that is exactly what they are saying. If that is the case, then I do not see what is the point of those vaccine trials\dots{} unless the end goal is something else. One thing is certain---the claim that the vaccines are required before life can go back to normal is bogus, as there will be no proof they have any effect on any of the serious outcomes preventing which we were told required the lockdowns and used as justification for the actual (hugely expensive) vaccine trials themselves.\textsuperscript{\cite{urle99aabeb}}

\begin{tcolorbox}[quote]

\dots{}\underLine{\textsb{The most advanced trials for coronavirus vaccines cannot tell researchers if the shots will save lives, or even if they'll prevent serious disease}}, a drug development expert pointed out Wednesday. \underLine{\textsb{The ongoing trials are only designed to show if the vaccines prevent infection---and most infections are mild infections}}, Peter Doshi, an associate editor at the \textit{BMJ} medical journal and a drug development specialist at the University of Maryland's school of pharmacy, said. \enquote{I think there are some pretty widely held assumptions about what we are getting out of Phase 3 studies,} Doshi told CNN. \enquote{\underLine{\textsb{None of the trials currently under way are designed to detect a reduction in any serious outcome such as hospital admissions, use of intensive care, or deaths}}. \underLine{\textsb{Nor are the vaccines being studied to determine whether they can interrupt transmission of the virus}},} Doshi wrote in the \textit{BMJ}.\textsuperscript{\cite{url0dd44589}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}\enquote{\underLine{\textsb{Hospital admissions and deaths from COVID-19 are simply too uncommon}} in the population being studied for an effective vaccine to demonstrate statistically significant differences in a trial of 30,000 people. \underLine{\textsb{The same is true of its ability to save lives or prevent transmission: the trials are not designed to find out}}.} Four vaccines being developed in the US are in the most advanced, Phase 3 stage of development: those being made by Moderna, Pfizer, AstraZeneca and Johnson \& Johnson. They're \enquote{event-driven} trials, meaning that the goal is to keep them going until a certain number of volunteers become infected. \underLine{\textsb{If more infections are seen among people who got placebo, or dummy shots, it's an indication the vaccines prevented infection. But that doesn't mean the vaccines saved people from serious disease or death}}, Doshi argued. \enquote{Severe illness requiring hospital admission, which happens in only a small fraction of symptomatic COVID-19 cases, would be unlikely to occur in significant numbers in trials,} he wrote.\textsuperscript{\cite{url0dd44589}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}\enquote{\underLine{\textsb{People expect that the most severe part of the Covid iceberg---the ICU admissions and hospitalizations and deaths---that's what a vaccine would put an end to}},} he said. \underLine{\textsb{but the current trials will just look for early infections}}. It's possible to keep these current trials going and add onto them so that they will, eventually, answer the question of whether Covid vaccines save lives and prevent severe disease.\textsuperscript{\cite{url0dd44589}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}