\chapter{Eli Lilly's Trial for COVID-19 Antibody Treatment Halted for Safety Reasons}
\tags{Antibodies, Coronavirus, COVID-19, Dangerous, Eli Lilly, Halted, Monoclonal, SAE, Serious Adverse Event, Side Effect, Trial}
\info{THREAD \#36832~\textbar{}~OCTOBER 13, 2020}

\begin{refsection}

Just, wow!

The bad news for the nascent COVID-19 industry just keep piling on. Just a a few hours ago I posted about the J\&J vaccine trial put on hold, and this was the second (out of 4 total) human trials put on hold.\textsuperscript{\cite{urle755db81}}

Now, we have another human trials put on hold due to a serious adverse event (SAE), but this time it is not a vaccine trial but a treatment trial using with a synthetic monoclonal antibody, similar to ones given to cancer patients by IV infusion. The monoclonal treatments are notorious for their severe side effects, which are sometimes lethal. To make matters worse, they often cause secondary cancer in patients using them as cancer treatments. I can't imagine FDA approving a COVID-19 treatment that has PML or cancer as a side effect, but we have been (unpleasantly) surprised by the FDA before so I don't have much hope this agency will do the right thing in a such a politically charged situation.

\begin{tcolorbox}[quote]

\dots{}\underLine{\textsb{Drugmaker Eli Lilly said Tuesday it is pausing its trial of a combination antibody treatment for coronavirus for safety reasons}}. \underLine{\textsb{Usually, clinical trials are paused because a volunteer has suffered a side effect or become ill}}, but the company did not say what happened. \enquote{Safety is of the (utmost) importance to Lilly,} a spokesperson told CNN by email. It said the trial's Data Safety Monitoring Board (DSMB), an independent group of medical experts who monitor clinical trials, recommended the pause.\textsuperscript{\cite{urlbad332a7}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}\underLine{\textsb{The trial, evaluating Lilly's investigational neutralizing antibody as a treatment for COVID-19 in hospitalized patients}}, is sponsored by the National Institute of Allergy and Infectious Diseases (NIAID), part of the National Institutes of Health (NIH). \enquote{Lilly is supportive of the decision by the independent DSMB to cautiously ensure the safety of the patients participating in this study,} the company said in the statement.\textsuperscript{\cite{urlbad332a7}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}