\chapter{More Japanese Suicides in October, Than COVID-19 Deaths in Entire 2020}
\tags{Anxiety, COVID-19, Death, Depression, Lockdown, Pandemic, Stress, Suicide}
\info{THREAD \#37554~\textbar{}~NOVEMBER 29, 2020}

\begin{refsection}

I know Japan is not the best comparison to the West due to their unique cultural attitude/tolerance towards suicides, especially in regards to people perceived to be \enquote{dishonored} due to falling on hard luck. However, it is still a stark reminded of what the lockdowns lead to and I suspect we may see similar numbers in Western countries over the next 1--2 years when the economic toll of the lockdowns fully dawns upon the general population. I am surprised to see CNN report on such issues, but I guess even they cannot afford to ignore reality all the time.

\begin{tcolorbox}[quote]

\dots{}The first time, she was just 22 years old with a full-time job in publishing that didn't pay enough to cover her rent and grocery bills in Tokyo.\textsuperscript{\cite{urlbb1a13f7}} \enquote{I was really poor,} said Kobayashi, who spent three days unconscious in hospital after the incident. Now 43, Kobayashi has written books on her mental health struggles and has a steady job at an NGO. But the coronavirus is bringing back the stress she used to feel. \enquote{My salary was cut, and I cannot see the light at the end of the tunnel,} she said. \enquote{I constantly feel a sense of crisis that I might fall back into poverty.} \underLine{\textsb{Experts have warned that the pandemic could lead to a mental health crisis}}. \underLine{\textsb{Mass unemployment, social isolation, and anxiety are taking their toll on people globally}}. \underLine{\textsb{In Japan, government statistics show suicide claimed more lives in October than COVID-19 has over the entire year to date}}. \underLine{\textsb{The monthly number of Japanese suicides rose to 2,153 in October, according to Japan's National Police Agency}}. \underLine{\textsb{As of Friday, Japan's total COVID-19 toll was 2,087}}, the health ministry said.\textsuperscript{\cite{url1ffa32f6}}

\end{tcolorbox}

BTW, before people try to explain this with something specific to Japan---their suicide rate declined \char`~30\% over the last decade. So, this is another strong sign that the shocking jump in suicide this year is lockdown-related.\textsuperscript{\cite{urlea1081cd}}


\printbibliography[heading=subbibliography]

\end{refsection}