\chapter{People Who Refuse the COVID-19 Vaccine May Be Banned Socially}
\tags{Ban, COVID-19, Mandatory, Refuse, Social Interaction, Vaccines, Work}
\info{THREAD \#37335~\textbar{}~NOVEMBER 15, 2020}

\begin{refsection}

And so it begins, at least in the UK/EU. When we first discussed this back in May here on the forum the majority of the comments were \enquote{You guys are nuts. Nobody is going to ban you from working, travelling or going to the bar if you don't get vaccinated.} Just as we also discussed, the narrative is that the vaccine is not going to be mandatory but, you know, there will be consequences if you do not vaccinate. No work, no travel, and no access to any social venues. In other words, refusing to vaccinate = life becomes impossible.

\begin{tcolorbox}[quote]

\dots{}\underLine{\textsb{People who refuse to get the coronavirus vaccine may face being banned from pubs, restaurants and even their places of work}}, according to a senior MP. Amid fears a small but vocal anti-vaxxer lobby in the UK may convince more people not to sign up for the jab, Conservative Tom Tugendhat has warned \underLine{\textsb{those who reject it may find it hard to return to normal life}}. Speaking to HuffPost UK's Commons People podcast, Mr Tugendhat said \underLine{\textsb{he could \enquote{certainly see the day} when people weren't allowed into the office until they could prove they'd had the vaccine}}. \underLine{\textsb{Venues may also demand to see vaccination certificates on the door before people are allowed inside}}, he said.\textsuperscript{\cite{urlc8f72595}}

\end{tcolorbox}

\begin{tcolorbox}[quote]

\dots{}\enquote{There was no debates, no appeals and no further requests. And I can see a situation where \underLine{\textsb{yes, of course you're free not to have the vaccine, but there are consequences}}.} Mr Tugendhat was asked on the podcast whether he thought public services like transport systems could also follow suit and ban people who haven't been vaccinated. He replied: \enquote{It would depend what the public services were, and who and when, so I wouldn't want to start predicting.} \enquote{\underLine{\textsb{but I do think that if things are shown to be safe then rejecting them when they have a wider effect on the whole of society is going to have consequences}}.}\textsuperscript{\cite{urlc8f72595}}

\end{tcolorbox}

\printbibliography[heading=subbibliography]

\end{refsection}