\chapter{The Failed Experiment of Covid Lockdowns}
\tags{Coronavirus, COVID-19, Disaster, Fraud, Ineffective, Lockdown, Pandemic, Virus}
\info{THREAD \#36285~\textbar{}~SEPTEMBER 06, 2020}

\begin{refsection}

Once again, the actual title of the article. Something is happening across MSM and I can't quite put my finger on it. One possibility is MSM is hedging its bets on a potential upcoming massive public backlash and lawsuits against govt and MSM over the fearmongering and fraud we have been enduring over the last 5--6 months.\textsuperscript{\cite{urlc495f420}}

With the IRS checks ending and now 40+ million unemployed, massive increase in suicides, drug/alcohol abuse, chronic diseases, etc. there is now tangible likelihood for physical violence against the spreaders of COVID-19 lies that led to so many people's livelihood/lives destroyed.\textsuperscript{\cite{url40d0c065}}

This view is supported by a statement from the quote below, which basically says \enquote{but\dots{} but\dots{} but\dots{} wE DidN'T kNoW iF tHe viRuS is DanGErouS sO We diD It tO ProTEcT yOU!.} There is also the possibility that MSM, and the power structures that rule us being hopelessly microcephalic (in Ray's words) and this worldwide fiasco being simply the result of the decisions of drooling simpletons. Frankly, I am not sure which option is worse---being constantly under attack from truly evil/deranged or monumentally stupid power structures. Ray seems to think that in medicine, it is mostly idiotism that drives the fiasco, as the doctors themselves are dropping like flies from their own \enquote{amazing} treatments. Maybe it is the same in politics\dots{}

\begin{tcolorbox}[quote]

\dots{}Six months into the COVID-19 pandemic, the U.S. has now carried out two large-scale experiments in public health---first, in March and April, the lockdown of the economy to arrest the spread of the virus, and second, since mid-April, the reopening of the economy. The results are in. \underLine{\textsb{Counterintuitive though it may be}}, statistical analysis shows that \underLine{\textsb{locking down the economy didn't contain the disease's spread and reopening it didn't unleash a second wave of infections}}. Considering that lockdowns are economically costly and create well-documented long-term public-health consequences beyond Covid, \underLine{\textsb{imposing them appears to have been a large policy error}}. \underLine{\textsb{At the beginning, when little was known, officials acted in ways they thought prudent}}. But now evidence proves that \underLine{\textsb{lockdowns were an expensive treatment with serious side effects and no benefit to society}}.\textsuperscript{\cite{url8ef3be3f}}

\end{tcolorbox}


\printbibliography[heading=subbibliography]

\end{refsection}